\Large \bf Frontrunning

### 2018-08-16 frontrunning/Latex/sections/paper.tex
[frontrunning] add charts and more detail for status ICO

%@shayan: make charts and figure out the orange seller

@@

% Proof of f2pool involvement: https://etherscan.io/address/0x5fb8373bf5086fb38ef0fb686b3092145de0d1c1
% funds come from f2pool and refunds goes back to f2pool again

@@

% this will include: The blocks mined by F2Pool, containing transactions (~100 ETH) to Status ICO, other blocks mined in that time period, the movement of status tokens from those addresses allegedly linked to F2Pool (or/and Yunbi in this case).
% https://github.com/corpetty/ICO_analysis/blob/master/status/Status.ipynb
% https://github.com/corpetty/py-etherscan-api

%What is Bancor and how it can be frontrun:%

\subsubsection{Bancor} %frontrunning by network participants.

>>>>

\begin{figure}[h]
\centering
\includegraphics[width=0.5\linewidth]{figures/Mining_pool_ratio.png}
\caption{The percentage of Ethereum blocks mined between block 3903900 and 3908029, this is the time frame in which Status.im ICO was running. This percentage roughly shows the hashing power ratio each miner had at that time. \label{fig:mining_pool_ratio}} % IS THIS STATEMENT CORRECT?
\end{figure}

F2Pool, an Ethereum mining pool that had around 23\% of the mining hash rate at the time (Figure ~\ref{fig:mining_pool_ratio}), sent 100 Ether to 30 new Ethereum addresses before Status.im ICO started. On the time the ICO started F2Pool constructed 31 transactions from the addresses they controlled to the ICO token sale smart contract without broadcasting these transactions to the network and focused their mining power to mine only their own transactions with some exceptions.
As shown in figure  ~\ref{fig:Transactions_miners_while_status_ico_cut}, most of the top miners in the mentioned time window, have mined almost the same number of failed and successful transactions which were directed toward Status.im token sale, however F2Pool's transaction indicate they successful transactions were equivalent to 10\% of the failed transactions, hence maximizing the mining rewards for them while censoring other transactions to the token sale smart contract.

\begin{figure}[h]
\centering
\includegraphics[width=0.5\linewidth]{figures/Transactions_miners_while_status_ico_cut.png}
\caption{This chart shows the miner behaviour on the time window that Status.im ICO was running. \label{fig:Transactions_miners_while_status_ico_cut}} 
\end{figure}

Involvement of F2Pool in this action becomes obvious when the transactions from these 30 addresses are traced. As shown in figure ~\ref{fig:f2poolfrontrun}, the funds deposited by F2Pool in these addresses where sent to Status.im ICO and mined by F2Pool. Once the dynamic ceiling algorithm refunded a portion of the sent funds back to these addresses, these funds were again sent back to F2Pool main address. 
%TODO: these need more details and proofs. ask Jeremy about how to go on about this!

@@

@@

%What is Bancor and how it can be frontrun:%
\subsubsection{Bancor} %frontrunning by network participants.
